\documentclass[10pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{dsfont}
\usepackage{amsmath, amsthm, amssymb, mathrsfs}
\usepackage[abbrev,non-sorted-cites]{amsrefs}
\usepackage[all]{xy}
\usepackage{CJK}
\usepackage{grffile}
\usepackage{graphicx}
\ProvidesPackage{stackrel}
\newtheorem{thm}{Theorem}[section]
\newtheorem{cor}[thm]{Corollary}
\newtheorem{lem}[thm]{Lemma}
\newtheorem{ex}[thm]{Example}
\newtheorem{definition}[thm]{Definition}
\newtheorem{rmk}[thm]{Remark}
\newtheorem{obs}[thm]{Observation}
\newtheorem{prop}[thm]{Proposition}
\newtheorem{conj}[thm]{Conjecture}
\newtheorem{question}[thm]{Question}
\newtheorem{prob}[thm]{Problem}
\renewcommand{\thefootnote}{\arabic{footnote}}

\newcommand{\de}{\partial}
\newcommand{\db}{\overline{\partial}}
\newcommand{\ov}{\overline}
\newcommand{\ddbar}{\sqrt{-1}\de\db}
\newcommand{\vp}{\varphi}
\newcommand{\ti}{\tilde}
\newcommand{\ve}{\varepsilon}
\newcommand{\Ric}{\mathrm{Ric}}
\newcommand{\tr}[2]{\textrm{tr}_{#1} #2}
\renewcommand{\leq}{\leqslant}
\renewcommand{\geq}{\geqslant}



\begin{document}

%\title{Geometry and Topology Problems}

%\maketitle

%\section*{Individual}

\begin{center}
S.-T. Yau College Student Mathematics Contests 2019

\vspace{0.1cm}

\Large {\bf Algebra and Number Theory}

\vspace{0.1cm}

\large {\bf Individual (5 problems)}

\vspace{0.1cm}
\end{center}

\begin{itemize}
\item[1)]Let $G$ be a finite group. Assume that for any representation $V$ of $G$ over a field of characteristic zero, the character $\chi_{_V}$ takes value in $\mathbb{Q}$.  Assume $g$ is an element in $G$ such that $g^{2019}=1$.

Prove that $g$ and $g^{19}$ are conjugate in $G$.



\item[2)] Let $p$ be a prime number, and let $\mathbb{F}_p$ be the finite field with $p$ elements.
Let $F=\mathbb{F}_p(t)$ be the field of rational functions over $\mathbb{F}_p$. Consider all subfields $C$ of $F$ such that $F/C$ is a finite Galois extension.

\begin{enumerate}
\item Show that among such subfields, there is a smallest one $C_0$, i.e., $C_0$ is contained in any other $C$.
\item What is the degree of $F/C_0$ ?
\end{enumerate}



\item[3)]Let $R\subset R'$ be an integral extension of commutative rings. Let $\mathfrak{p}'$ be a prime ideal of $R'$. Prove that $\mathfrak{p}'$ is a maximal ideal of $R'$ if and only if $\mathfrak{p}'\cap R$ is a maximal ideal of $R$.


\item[4)]
\begin{enumerate}
\item Prove that $\mathrm{GL}_n(\mathbb{C})$ is path-connected.
\item Let
 $$X=\{A\in\mathrm{GL}_n(\mathbb{C})\,|\, A^m=\mathrm{Id}\},$$
Describe the path-connected component of $X$ and prove your answer.
\end{enumerate}


\item[5)]


The Fibonacci sequence is defined by
$$F_0=0, \quad F_1=1, \quad F_{n+2}=F_{n+1}+F_n.$$
Let $p$ be a prime number.

\begin{enumerate}
\item Show that if $p\equiv 1, 4\ (\text{mod }5)$, then $p$ divides $F_{p-1}$.
\item Let $\mathbb{F}_{p^2}$ be the finite field of $p^2$ elements. Show that the norm map $N:\mathbb{F}^\times_{p^2}\to \mathbb{F}^\times_p$ is surjective, and deduce the cardinality of the kernel of $N$.
\item Show that if $p\equiv 2, 3\ (\text{mod }5)$, then $p$ divides $F_{p+1}$.
\end{enumerate}
\end{itemize}



\end{document}
